---
output: rmarkdown::github_document
---

# hosperf

Tools to Query Data from the Australian Institute of Health and Welfare'MyHospitals' Portal

## Description

More than 1,000 public and private hospitals across Australia have performance data available on 'MyHospitals' (<www.myhospitals.gov.au/>). Methods are provides to query indicators for available hospitals over time.

## What's Inside The Tin

The following functions are implemented:

- `get_datasets`:	Returns a custom dataset of a requested set of indicators for all available hospitals over a given time frame.
- `get_hospitals`:	Returns a data frame of all (public) hospitals with data in the MyHospitals website.
- `get_indicators`:	Returns a data frame of all indicators measured within the MyHospitals website.

NOTE: The endpoints are memoised to save the API bandwidth/CPU and due to the low likelihood of the data changing in-analysis session.

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/hosperf")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(hosperf)
library(tidyverse) # lazy since it's just for better printing

# current verison
packageVersion("hosperf")

```

```{r}
get_hospitals()
```

```{r}
get_indicators()
```

```{r}
glimpse(get_datasets(111, "2013-06"))
```
